Variants on the Flight and Maintenance Planning problem

### 2018-07-16 latex/notes/complexite/FMP_variants.tex
small changes to complexity format

    $\mathcal{P}_{ref}$:

@@

    $\mathcal{P}_{FMP}$:

@@

    \begin{tabular}{l|l|l}
    	\textbf{FMP}    &  \textbf{Meaning} & \textbf{f(I)} \\ \hline
        $\mathcal{T}$    &  Planning horizon. & $\{\min_p({s_p}) ... \max_p({f_p})\}$ \\
        $\mathcal{I}$    &  Resources. & $ \mathcal{E}$ \\
        $\mathcal{J}$    &  Tasks.  & $ P$ \\
        $\mathcal{T}_j$  &  time periods in which task $j$ is active. & $t \in \{s_p ... f_p\}$ \\
        $\mathcal{J}_t$  &  tasks to be realized in period $t$. & $j | t \in \{s_p ... f_p\}$ \\
        $\mathcal{I}_j$  &  resources that can be assigned to task $j$. & $E_p$\\
        $\mathcal{O}_i$  &  tasks for which resource $i$ can be used. & $P_i$ \\
        $\mathcal{T}^{s}_t$ &  time periods $t' \in \mathcal{T}$ that control de maintenance starts. & $\{\}$ \\
    \end{tabular}

@@

    \begin{tabular}{l|l|l}
    	\textbf{FMP}    &  \textbf{Meaning} & \textbf{f(I)} \\ \hline
        $D_t$            & number of resources to be assigned in total in period $t$ & $|\mathcal{J}_t|$\\
        $A^{min}_j$      & minimum number of consecutive periods for task $j$. & $u_p$ \\
        $Ret^{Init}_{i}$ & remaining elapsed time for resource $i$ at the start. & $|\mathcal{T}| + 1$ \\
        $R_{j}$          & Need of resources for task $j$ & $1$ \\
        $H_j$             & amount of resource time required by task $j$. & $ 0$ \\
        $M$               & maintenance duration in number of periods. & $ 0$ \\
        $E$               & remaining elapsed time after a maintenance. & $ 0$ \\
        $H$               & remaining usage time after a maintenance.& $ 0$ \\
        $N_t$             & number of resources in already-planned maintenances in period $t$ at the start. & $0$ \\
        $Rut^{Init}_{i}$  & remaining usage time for resource $i$ at the start of the planning horizon. & $ 0$ \\
        $Ret^{Init}_{sum}$& sum of remaining elapsed times at the start of the planning horizon. & $ 0$\\
        $Rut^{Init}_{sum}$& sum of remaining elapsed time at the start of the planning horizon. & $ 0$ \\
    \end{tabular}

>>>>

    $i \in \mathcal{P}_{ref}$:

@@

    $I(i \in \mathcal{P}_{FMP})$:

@@

    \begin{tabular}{l|l|l}
    	\textbf{FMP}    &  \textbf{Meaning} & \textbf{I(i)} \\ \hline
        $\mathcal{T}$    &  Planning horizon. & $\{\min_p({s_p}) ... \max_p({f_p})\}$ \\
        $\mathcal{I}$    &  Resources. & $ \mathcal{E}$ \\
        $\mathcal{J}$    &  Tasks.  & $ P$ \\
        $\mathcal{T}_j$  &  time periods in which task $j=p$ is active. & $t \in \{s_p ... f_p\}$ \\
        $\mathcal{J}_t$  &  tasks to be realized in period $t$. & $j | t \in \{s_p ... f_p\}$ \\
        $\mathcal{I}_j$  &  resources that can be assigned to task $j=p$. & $E_p$\\
        $\mathcal{O}_i$  &  tasks for which resource $i=e$ can be used. & $P_e$ \\
        $\mathcal{T}^{s}_t$ &  time periods $t' \in \mathcal{T}$ that control de maintenance starts. & $\{\}$ \\
    \end{tabular}

@@

    \begin{tabular}{l|l|l}
    	\textbf{FMP}    &  \textbf{Meaning} & \textbf{I(i)} \\ \hline
        $D_t$            & number of resources to be assigned in total in period $t$ & $|\mathcal{J}_t|$\\
        $A^{min}_j$      & minimum number of consecutive periods for task $j=p$. & $u_p$ \\
        $Ret^{Init}_{i}$ & remaining elapsed time for resource $i$ at the start. & $|\mathcal{T}| + 1$ \\
        $R_{j}$          & Need of resources for task $j$ & $1$ \\
        $H_j$             & amount of resource time required by task $j$. & $ 0$ \\
        $M$               & maintenance duration in number of periods. & $ 0$ \\
        $E$               & remaining elapsed time after a maintenance. & $ 0$ \\
        $H$               & remaining usage time after a maintenance.& $ 0$ \\
        $N_t$             & number of resources in already-planned maintenances in period $t$. & $0$ \\
        $Rut^{Init}_{i}$  & remaining usage time for resource $i$ at the start of the planning horizon. & $ 0$ \\
        $Ret^{Init}_{sum}$& sum of remaining elapsed times at the start of the planning horizon. & $ 0$\\
        $Rut^{Init}_{sum}$& sum of remaining elapsed time at the start of the planning horizon. & $ 0$ \\
    \end{tabular}

$Q_{ref}$: For an instance $i \in \mathcal{P}_{ref}$, $\exists$ a solution with the number of resources $\leq k$:

$Q_{FMP}$: For an instance $I(i \in \mathcal{P}_{ref})$, $\exists$ a solution with the number of available resources $\geq |I| - k$:
